An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-06-03 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy updated text and code

NPC is the total present value of a time series. The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an interest rate of internal rate of return (IRR).[90]

LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost is considered [91]. LCOE method is useful in comparing different generation technologies with different operating characteristics [6].

LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value [92]. Eq.~\ref{eq:LCC} is used to calculate LCC of a PV system,
\begin{equation}
\label{eq:LCC}
LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
\end{equation}
\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs in present worth.

@@

Regarding financial analysis:
\begin{itemize}
	\item LCOE lifetime considered: 20 years;
	\item Battery lifetime: 4 years for lead-acid batteries. Therefore will be performed three battery bank replacements;
	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost [Agrener2013];
	\item Electrical protection and complementary electrical item: 7\% of equipment cost [Agrener2013]. Includes circuit breakers, surge protection devices, electrical grounding, DC fuses, main switchboard, string boxes;
	\item Value of the discount rate or interest rate: 10\%, what is a good rate considering financial investments in developing countries;
	\item Operation and maintenance costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of USD [Agrener2013].
\end{itemize}

>>>>

NPC is the total present value of a time series. The net present worth is found by discounting all cash inflows and outflows, including cost of installation, replacement and maintenance of the PV system, at an interest rate of internal rate of return (IRR)~\cite{Park2004}.

LCOE is defined as the average cost per kWh of useful electrical energy produced by the PV system when a lifetime, investment cost, replacement, operation and maintenance, and capital cost is considered~\cite{Kamel2005}. LCOE method is useful in comparing different generation technologies with different operating characteristics~\cite{Zhou2010}.

LCC is the estimation of sum of installation cost, operating and maintenance of a PV system for a period of time, and expressed in today's value~\cite{Applasamy2011}. Eq.~\ref{eq:LCC} is used to calculate LCC of a PV system,
\begin{equation}
\label{eq:LCC}
LCC = C_{PV} + C_{bat} + C_{charger} + C_{inv} + C_{installation} + C_{batrep} + C_{PWO\&M},
\end{equation}
\noindent where $C_{PV}$ is PV array cost, $C_{bat}$ is initial cost of batteries, $C_{charger}$ is cost of charger, $C_{inv}$ is inverter cost, $C_{installation}$ is installation cost, $C_{batrep}$ is battery replacement cost in present value, and $C_{PWO\&M}$ is operation and maintenance costs in present worth.

@@

Regarding financial analysis:
\begin{itemize}
	\item LCOE lifetime considered: 20 years;
	\item Battery lifetime: 4 years for lead-acid batteries. Therefore will be performed three battery bank replacements;
	\item Installation costs: includes delivery at the isolated community and installation costs itself, 5\% of total cost~\cite{Agrener2013};
%	\item Electrical protection and complementary electrical item: 7\% of equipment cost [Agrener2013]. Includes circuit breakers, surge protection devices, electrical grounding, DC fuses, main switchboard, string boxes;
	\item Value of the discount rate or interest rate: 10\%, what is a good rate considering financial investments in developing countries;
	\item Operation and maintenance annual costs: based on past PV projects in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\citep{Agrener2013}.
\end{itemize}
